A free/open-source Kazakh-Tatar machine translation system

### 2013-04-07 paper/paper.tex
stupid typo

\subsection{Morphotactic differences}
2 or 3 specific examples
\subsection{Lexical and morphological differences}
2 or 3 specific examples
\subsection{Syntactic differences}
%2 or 3 specific examples
There aer a number of syntactic differences in Tatar and Kazakh, which include differences in verb valencies in equivalent translations, FIXME, and FIXME.

>>>>

\subsection{Morphotactic differences}
2 or 3 specific examples
\subsection{Lexical and morphological differences}
2 or 3 specific examples
\subsection{Syntactic differences}
%2 or 3 specific examples
There are a number of syntactic differences in Tatar and Kazakh, which include differences in verb valencies in equivalent translations, FIXME, and FIXME.
